---
title: "W12 Case Study"
author: "Maddy McGreer"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)
library(USAboundaries)
library(sf)
library(ggplot2)
library(ggrepel)
library(leaflet)
```

```{r load_data}
# Use this R-Chunk to import all your datasets!


```

## Background

_Use leaflet to recreate the visualizations of the US map and counties._

## Data Wrangling

```{r tidy_data}
# Use this R-Chunk to clean & wrangle your data!
state_shape <- us_states() %>% 
  filter(jurisdiction_type == "state", 
         state_abbr != "AK", 
         state_abbr != "HI")

county_shape <- us_counties(states = "ID")

city_data <- us_cities() %>%
  filter(state_abbr != "AK",
         state_abbr != "HI")%>%
  arrange(desc(population)) %>%
  mutate(rank = as.integer(row_number()))

top_cities <- city_data %>%
  filter(rank <= 50)

top_cities$rank <- as.factor(top_cities$rank)

top_cities <- top_cities %>%
  mutate(lon = st_coordinates(geometry)[, "X"],
         lat = st_coordinates(geometry)[, "Y"])

```

## Data Visualization

```{r plot_data}
# Use this R-Chunk to plot & visualize your data!

## Create Leaflet Map
leaflet() %>%
  addTiles() %>%
  addPolygons(data = state_shape, color = "black", fill = "transparent") %>%
  addPolygons(data = county_shape, fill = "transparent", color = "grey") %>%
  addCircleMarkers(data = top_cities, lng = ~lon, lat = ~lat, color = "blue", radius = 2) %>%
  addLabelOnlyMarkers(data = top_cities, lng = ~lon, lat = ~lat, label = ~name_2010, labelOptions = labelOptions(noHide = TRUE)) %>%
  addLegend(position = "bottomright", colors = "blue", labels = "Population") 




```

## Conclusions

_In the `plot_data` chunk, I've replaced the `geom_point` and `geom_label_repel` layers with the corresponding leaflet functions._

_`geom_point` is replaced with `addCircleMarkers`, which adds circular markers to the leaflet map. The `lng` and `lat` arguments specify the longitude and latitude columns from the `top_cities` dataset._
_`geom_label_repel` is replaced with `addLabelOnlyMarkers`, which adds label markers to the leaflet map. The `lng` and `lat` arguments specify the longitude and latitude columns from the `top_cities` dataset, and the `label` argument specifies the column with the labels (`name_2010` in this case)._

