---
title: "W09 Case Study - It's About Time"
author: "Maddy McGreer"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: center
  pdf_document:
    toc: yes
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)
library(ggplot2)
library(lubridate)
library(riem)

```

```{r load_data}
# Use this R-Chunk to import all your datasets!

sales_data <- read.csv ("https://byuistats.github.io/M335/data/sales.csv")

```

## Background

_We have transaction data for a few businesses that have been in operation for three months. Each of these companies has come to your investment company for a loan to expand their business. Your boss has asked you to go through the transactions for each business and provide daily, weekly, and monthly gross revenue summaries and comparisons. Your boss would like a short write-up with tables and visualizations that help with the decision of which company did the best over the three-month period. You will also need to provide a short paragraph with your recommendation after building your analysis._

## Data Wrangling

```{r tidy_data}
# Use this R-Chunk to clean & wrangle your data!

# Convert time from UTC to MST
sales_data$Time <- with_tz(ymd_hms(sales_data$Time), "MST")

# Remove rows with missing or invalid values
sales_data <- na.omit(sales_data)



```

## Data Visualization

```{r plot_data}
# Use this R-Chunk to plot & visualize your data!

# Aggregate data at the daily level
daily_revenue <- sales_data %>%
  mutate(date = as_date(date(Time))) %>%
  group_by(Name, date) %>%
  summarise(revenue = sum(Amount)) %>%
  ungroup()

# Aggregate data at the weekly level
weekly_revenue <- sales_data %>%
  mutate(week = floor_date(Time, "week")) %>%
  group_by(Name, week) %>%
  summarise(revenue = sum(Amount)) %>%
  ungroup()

# Aggregate data at the monthly level
monthly_revenue <- sales_data %>%
  mutate(month = floor_date(Time, "month")) %>%
  group_by(Name, month) %>%
  summarise(revenue = sum(Amount)) %>%
  ungroup()

# Visualization: Gross revenue over time (daily)
ggplot(daily_revenue, aes(x = date, y = revenue, color = Name)) +
  geom_line() +
  labs(title = "Gross Revenue Over Time (Daily)",
       x = "Date", y = "Revenue") +
  theme_minimal()

# Visualization: Gross revenue over time (weekly)
ggplot(weekly_revenue, aes(x = week, y = revenue, color = Name)) +
  geom_line() +
  labs(title = "Gross Revenue Over Time (Weekly)",
       x = "Week", y = "Revenue") +
  theme_minimal()

# Visualization: Gross revenue over time (monthly)
ggplot(monthly_revenue, aes(x = month, y = revenue, color = Name)) +
  geom_line() +
  labs(title = "Gross Revenue Over Time (Monthly)",
       x = "Month", y = "Revenue") +
  theme_minimal()




```

```{r}
# Count the number of transactions per company
customer_traffic <- sales_data %>%
  group_by(Name) %>%
  summarise(traffic = n_distinct(Amount)) %>%
  ungroup()

# Visualization: Customer traffic per company
ggplot(customer_traffic, aes(x = Name, y = traffic)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Customer Traffic per Company",
       x = "Company", y = "Number of Transactions") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}
# Extract hour from the time
sales_data$hour <- hour(sales_data$Time)

# Visualization: Hours of operation per company
ggplot(sales_data, aes(x = hour, fill = Name)) +
  geom_histogram(binwidth = 1) +
  labs(title = "Hours of Operation per Company",
       x = "Hour", y = "Number of Transactions") +
  theme_minimal() +
  theme(legend.position = "top")

```

## Conclusions
_After analyzing the data I would say that the company that did best over a 3-month period would be HotDiggity. HotDiggity generated the most revenue and was second in customer traffic._
