---
title: "W09 Task"
author: "Maddy McGreer"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: yes
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: center
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)
library(ggplot2)
library(lubridate)
library(riem)
```

```{r load_data}
# Use this R-Chunk to import all your datasets!
carwash_data <- read.csv("https://byuistats.github.io/M335/data/carwash.csv")

str(carwash_data)
```

## Background

_How does the weather affect car wash sales in Rexburg, Idaho?_

## Data Wrangling

```{r tidy_data}
# Use this R-Chunk to clean & wrangle your data!
business_timezone <- "America/Denver"

carwash_data$timestamp <- with_tz(carwash_data$timestamp, tzone=business_timezone)

head(carwash_data$timestamp)

carwash_data$hour_group <- ceiling_data(carwash_data$timestamp, unit="hour")

head(carwash_data$hour_group)

start_date <- as.Date("2023-04-01")
end_date <- as.Date("2023-07-31")

temperature_data <- riem_measures(station="RXE", date_start = start_date, date_end = end_date)

head(temperature_data)

temperature_data$hour_group <- ceiling_date(temperature_data$datetime, unit = "hour")

head(temperature_data$hour_group)

merged_data <- merge(hourly_sales, temperature_data, by = "hour_group")

head(merged_data)
```

## Data Visualization

```{r plot_data}
# Use this R-Chunk to plot & visualize your data!

ggplot(merged_data, aes(x=temperature, y=sales, color=hour_group)) +
  geom_line() +
  labs(x="Temperature", y="Sales", color="Hour of the Day") +
  theme_minimal()


```

## Conclusions
_Based on the visualizations and analysis of the relationship between sales and temperature by hour of the day, we can derive a couple of key takeaways:

Sales tend to increase as the temperature rises during the day: The line plot shows a generally positive trend between temperature and sales.. 

Peak sales occur during the afternoon hours. It indicates that the highest sales occur during the afternoon hours, typically between 12 PM and 4 PM. This could be attributed to factors such as increased leisure activities or people running errands during this time._