
---
title: "W10 Task"
author: "Maddy McGreer"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: center
  pdf_document:
    toc: yes
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(quantmod)
library(dygraphs)
library(DT)
```

```{r load_data}
# Use this R-Chunk to import all your datasets!
setSymbolLookup(SPY='yahoo',VXN=list(name='^KR',src='yahoo'))


```


## Background

_The US Grocer: KR_
_A visualization of Kroger's performance in the past 5 years._

## Data Wrangling

```{r tidy_data}
# Use this R-Chunk to clean & wrangle your data!

# Kroger's performance in the past 5 years
# Define the start and end dates for the five-year period
start_date <- as.Date(Sys.Date() - 5 * 365)
end_date <- Sys.Date()

# Fetch the historical stock price data for Kroger (KR)
kr <- getSymbols("KR", from = start_date, to = end_date, auto.assign = TRUE)

# Extract the adjusted closing prices
kr_prices <- Ad(KR)

# Create a data frame with date and price columns
kr_data <- data.frame(Date = index(kr_prices), Price = kr_prices)
```

```{r}
datatable(kr_prices)
```


```{r}
# Plot the stock price performance for the past 5 years
dygraph(kr_prices, main = "Kroger (KR) Stock Price Performance",
        ylab = "Stock Price") %>%
  dyRangeSelector()



```

## Data Visualization

```{r}
# Use this R-Chunk to plot & visualize your data!
# Define the start and end dates for the two-year period
start_date <- as.Date(Sys.Date() - 2 * 365)
end_date <- Sys.Date()

# Fetch the historical stock price data for Kroger
kr <- getSymbols("KR", from = start_date, to = end_date, auto.assign = FALSE)

# Extract the adjusted closing prices
kr_prices <- Ad(kr)

# Calculate the performance relative to the initial investment
initial_investment <- 10000
kr_performance <- kr_prices / kr_prices[1] * initial_investment

# Create DF
kr_data <- data.frame(Date = index(kr_prices), Performance = kr_performance, row.names = NULL)

```

```{r}
datatable(kr_performance)
```


```{r plot_data}
# Plot the performance of Kroger stock using dygraph
dygraph(kr_data, main = "Kroger (KR) Stock Performance", group = "stock", ylab = "Performance ($)") %>%
  dyRangeSelector() %>%
  dyRebase(initial_investment)

```

## Conclusions
_In the Kroger (KR) stock performance graph, I utilized the dygraph package in R to present the stock's performance over a two-year period. The graph is presented on a timeline axis, showcasing the price changes over time. To provide a meaningful comparison, I used the dyRebase function to rebase the stock performance to $10,000, allowing for a clear assessment of the investment's relative growth._




